Diagnostics

### 2020-07-15 output_scripts/Diagnostics.Rmd
finish plots for paper

@@

@@

```{r cohort-1,cache=TRUE}
current_cohort <- 1
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-2,cache=TRUE}
current_cohort <- 2
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-3,cache=TRUE}
current_cohort <- 3
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-4,cache=TRUE}
current_cohort <- 4
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-5,cache=TRUE}
current_cohort <- 5
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-6,cache=TRUE}
current_cohort <- 6
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-7,cache=TRUE}
y.upper <- 80
current_cohort <- 7
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-8,cache=TRUE}
current_cohort <- 8
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-9,cache=TRUE}
y.upper <- 60
current_cohort <- 9
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-10,cache=TRUE}
current_cohort <- 10
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

>>>>

path_change <- FALSE # if change the data path, set this to false, else TRUE

@@

<!-- # Correlation Issues in Fits -->

<!-- We seek to further -->

@@

```{r cohort-1,cache=path_change}
current_cohort <- 1
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-2,cache=path_change}
current_cohort <- 2
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-3,cache=path_change}
current_cohort <- 3
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-4,cache=path_change}
current_cohort <- 4
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-5,cache=path_change}
current_cohort <- 5
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-6,cache=path_change}
current_cohort <- 6
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-7,cache=path_change}
y.upper <- 80
current_cohort <- 7
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-8,cache=path_change}
current_cohort <- 8
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-9,cache=path_change}
y.upper <- 60
current_cohort <- 9
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

```{r cohort-10,cache=path_change}
current_cohort <- 10
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))
